A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
grammar

We see here that the sample variance generally decreases or has no association with the grain yield.
This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is a the more generic error term.

>>>>

We see here that the sample variance generally decreases or has no association with the grain yield.
This might be due to the unpredictable nature of mungbeans, however going forward we will use mean squares which defines between trial variation and is the more generic error term.
